Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-01-20 Tex/LaTeX2e Style File/Trindade_Cordeiro_IEEE_SE_rev0.tex
SE paper update

\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
\IEEEcompsocthanksitem{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}}% <-this % stops a space
\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017), for the financial support.}
\thanks{Manuscript received November 23, 2018; revised XXXXX 11, 2019.}}

@@

% The paper headers
\markboth{IEEE Transactions on Computers,~Vol.~14, No.~8, August~2015}%
{Trindade \MakeLowercase{\textit{et al.}}: Automated Verification of Stand-Alone Solar Photovoltaic Systems}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
This paper makes two original contributions. % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
Firstly, we propose an automated verification method that formally checks the design of a given PV system using incremental model checking based on Satisfiability Module Theories (SMT), and that was never did before. Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.

@@

%------------------------------------------
\subsection{Description of the Case Studies}
%------------------------------------------

We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).

@@

All experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning our verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 \phantom{}-boolector}. 
% enabled with the goal of reducing memory usage; 
We have also used the SMT solver Boolector version 2.4.1~\cite{Brummayer}. %The experiments were performed without a predefined timeout.

@@

The same five case studies were evaluated by HOMER Pro. The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed by HOMER Pro. Fig. \ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software.

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{homer.png}
\centering
\caption{Homer simulation screen.}
\label{fig:homerscreen}
\end{figure}
%
Despite the divergence of results for the houses 2, 3 and 4 w.r.t. our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2. House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
%
%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components. Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions. The season has impact since the case studies are from the rain forest, where clouds are always present. As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

>>>>

\author{Alessandro~Trindade and Lucas~Cordeiro% <-this % stops a space
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem{A. Trindade is with the Department of Electricity, Federal University of Amazonas, Manaus, Brazil, e-mail: alessandrotrindade@ufam.edu.br.}% <-this % stops a space
\IEEEcompsocthanksitem{L. Cordeiro is with School of Computer Science, The University of Manchester, UK, e-mail: lucas.cordeiro@manchester.ac.uk.}}% <-this % stops a space
\thanks{The authors would like to thank Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, call 009/2017 and PROTI Pesquisa 2018), for the financial support.}
\thanks{Manuscript received January 23, 2019; revised XXXXX 11, 2019.}}

@@

% The paper headers
\markboth{IEEE Transactions on Software Engineering,~Vol.~XX, No.~YY, August~2019}%
{Trindade and Cordeiro: Automated Verification of Stand-Alone Solar Photovoltaic Systems}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

@@

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
\textit{Novelty Statement:} This paper makes two original contributions. % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
Firstly, we propose an automated verification method that formally checks the design of a given PV system using model checking based on Satisfiability Module Theories (SMT), and that was never did before. Secondly, experimental results show that this proposed approach can find subtle design errors in PV systems, which are not easily detected by other approaches based on simulation.

@@

%------------------------------------------
\subsection{Description of the Case Studies}
%------------------------------------------
We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (three in series 325W PV panels, four 220 Ah batteries in a configuration with two series and two parallel with 48h autonomy, 700 W inverter with surge of 1,600W, charge controller with MPPT with 35A/150V of capacity) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with four 325W PV panels in a configuration two series and two parallel, four 120Ah batteries in series and autonomy of just 6 h, 1,200 W inverter with surge of 1,600 W, charge controller with MPPT of 150V/35A).

@@

All experiments were conducted on an otherwise idle Intel octa core Xeon CPU E5-2640 with 2.4 GHz and 264 GB of RAM, running Ubuntu 18.04.1 LTS 64-bits. Concerning our verification engine, ESBMC v6.0.0 was used \footnote{The command-line used to perform the verification is: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-no-div-by-zero-check -\phantom{}-unwind 300 -\phantom{}-boolector}. 
% enabled with the goal of reducing memory usage; 
We have also used the SMT solver Boolector version 2.4.1~\cite{Brummayer}. %The experiments were performed without a predefined timeout.

@@

The same five case studies were evaluated by HOMER Pro. The simulation results showed that the project restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance related issues. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed by HOMER Pro. Fig. \ref{fig:homerscreen} shows one of the screens presented by HOMER Pro software, specifically to house 1.

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{homer.png}
\centering
\caption{HOMER simulation screen (evaluation 30-days version).}
\label{fig:homerscreen}
\end{figure}
%
Despite the divergence of results for the houses 2, 3 and 4 w.r.t. our proposed approach, it is evident that the information collected from the dwellers and from the monitoring systems indicate that our approach provides the correct evaluation of the PV system, thus answering RQ2. House 5 presented flaws from both tools; however, only our approach indicated which design error was responsible for the flaw (number of PV panels), further answering RQ2.
%
%Note that a PV design always uses daily average values of sun hours to each site, with impact in the PV components. Those hours are based on historical data and, in field, it is not unusual to find days where that number of hours was not reached due to weather conditions. The season has impact since the case studies are from the rain forest, where clouds are always present. As a result, the identified flaws in houses 1, 2, 3, and 4, are justified once again.
%
%We have evaluated five case studies in total using the HOMER Pro tool and our automated verification tool. Related to the HOMER Pro, the simulation, based on NASA data from the deployed systems (temperature and solar irradiance), shows that the restrictions were met by four 700 W PV systems (house 1, 2, 3 and 4), without any indication of sizing error or even performance. The case study that was unsuccessful during simulation was the 1,200 W (house 5); however, without any indication about the failures of this PV system. All the simulations took less than 5 seconds (each) to be performed.
%
%However, related to the results of the automated verification: (a) the 1,200 W PV system (house 5) failed during the sizing check. The number of panels was \textit{incorrect}; in particular, the counterexample provided by our verification method indicated 3 panels in parallel and the sized project has 2 in series and 2 in parallel. That verification took 63.3 hours to be performed. Surveying the owner of the 1,200 W system it was identified that, in fact, the system mostly of the time do not met the battery autonomy (mainly when all the loads are turned on). That behavior is expected because the system was purchased as an off-the-shelf solution and not as a specific design for the electrical charges of the house; (b) Related to the four 700 W PV systems, just one verification finished its analysis (house 1) considering the time-out of 432 h of computing. The sizing check was successful during automated verification, but there was found flaw related with the battery autonomy, when SOC reached levels below of 75\%. The automated verification identified the flaw right after the first night-discharge cycle, before the solar system start to recharge the batteries. The proposed tool took 409.3 hours to find this error at house 1. This possible flaw was confirmed with the dweller that uses the system: at least once or twice a mouth is usual the system to turn off, normally during raining days or with more clouds in the sky, and after the sun rises the system returns to normal operation. Related to houses 2, 3 and 4, it was considered that the automated verification had a time-out condition, with no conclusive results.

### 2019-01-20 Tex/LaTeX2e Style File/cover-letter-SE.tex
SE paper update

\begin{flushleft}
      Badrul H. Chowdhury,  Ph.D. \\
	Editor-in-Chief \\
	University of North Carolina at Charlotte \\
	IEEE Transactions on Sustainable Energy 
    \end{flushleft}

\indent Dear Badrul
\vi

Please find enclosed our manuscript entitled as ``Automated Verification of Stand-alone Solar Photovoltaic Systems'' by Alessandro Trindade and Lucas Cordeiro which we would like to submit for publication in the journal of IEEE Transactions on Sustainable Energy.

>>>>

\begin{flushleft}
	Nenad Medvidovic \\
	Editor-in-Chief \\
	University of Southern California\\
	Viterbi School of Engineering, Department of Computer Science \\
	941 Bloom Walk, SAL 338, Los Angeles, CA 90089-0781 \\
	IEEE Transactions on Software Engineering 
    \end{flushleft}

\indent Dear Nenad
\vi

Please find enclosed our manuscript entitled as ``Automated Verification of Stand-alone Solar Photovoltaic Systems'' by Alessandro Trindade and Lucas Cordeiro which we would like to submit for publication in the journal of IEEE Transactions on Software Engineering.
